---
title: "Social Science R"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SocialScienceR

<!-- badges: start -->
<!-- badges: end -->

The goal of SocialScienceR is to create a package that teaches social scientists who are not comfortable with coding how to use R for data analysis and visualization. 

## Installation

You can install the development version of SocialScienceR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("margotdv04/SocialScienceR")
```

## Purpose

SocialScienceR is a package that will teach users how to use R for data analysis and visualization.

## Target Audience

The target audience for SocialScienceR are social scientists who are not comfortable with coding for data analysis.


## Example

You can load SocialScienceR using the `library()` function.
```{r example}
library(SocialScienceR)
```

SocialScienceR comes preloaded with data on democracy, human development index, and happiness worldwide.

```{r}
head(country_indicators)
```

SocialScienceR also teaches users how to use basic R functions. Here's an example of the view_data() function, which teaches users how to view data loaded in the package in the console.

<iframe
    width="560"
    height="315"
    src="https://www.youtube.com/embed/L7CdsK5cb5E"
    frameborder="0"
    allow="autoplay; encrypted-media"
    allowfullscreen
>
</iframe>

## Proposed R Package

Our proposed R package is what we have described above, a package that teaches social scientists how to use R. We plan to continue this project and expanding its breadth. 

## Contributors

[Margot Draillard-Vandenberg](https://github.com/margotdv04)


[Esa Schenck](https://github.com/esaschenck)
